Using the internal language of toposes in algebraic geometry

### 2015-11-26 slides-ihes2015.tex
Credit where credit is due
Slide on the gros Zariski topos

  {\vspace{-0.5em}\centering
  \includegraphics[scale=0.3]{images/external-internal-small}
  \par\medskip}

  \begin{itemize}
    \item Simplify routine proofs.
    \item Gain conceptual clarity.
    \item Develop a synthetic account of scheme theory.
  \end{itemize}
\end{frame}
% Fun facts:
% Take O_X, pullback along X_{negneg} --> X, pushforward: result is K_X.
% Very naive definition of P^n works internal to the big Zariski topos.

@@

>>>>

  {\vspace{-0.5em}\centering
  \rotatebox{90}{\tiny\scalebox{0.5}{Illustration: Carina Willbold}}\hspace{-0.05cm}%
  \includegraphics[scale=0.3]{images/external-internal-small}
  \par\medskip}

  \begin{itemize}
    \item Simplify proofs.
    \item Gain conceptual clarity.
    \item Develop a synthetic account of scheme theory.
  \end{itemize}
\end{frame}
% Fun facts:
% Take O_X, pullback along X_{negneg} --> X, pushforward: result is K_X.
% Very naive definition of P^n works internal to the big Zariski topos.

@@

\begin{frame}\frametitle{The gros Zariski topos}
  Let~$X$ be a scheme. The \hil{gros Zariski topos} is the topos of sheaves
  on~$\Sch/X$ with respect to the Zariski topology. From its point of view,
  \ldots

  \begin{itemize}
    \item \ldots{} $X$-schemes look just like sets,
    \item \ldots{} $\mathbb{P}^n_X$ is given by the naive expression
    \[ \{ (x_0,\ldots,x_n) \,|\, x_1 \neq 0 \vee \cdots \vee x_n \neq 0
    \}/\text{(rescaling)}, \]
    \item \ldots{} affinity is a ``double dual condition'', and
    \item \ldots{} the étale topology is the coarsest topology~$\Diamond$ such
    that
    \[ \forall f : \mathbb{A}^1_X[T]\_
      \text{$f$ is separable} \Rightarrow
      \Diamond(\exists t : \mathbb{A}^1\_ f(t) = 0). \]
  \end{itemize}
\end{frame}
